---
title: "Location & Date reporting bias"
output: html_document
params:
  path: C:\Users\LOCAL_~3\Temp\RtmpkPFN75\file478c6bfd7478
  extra_missing_types: c()
  location_variable: Owning Unit
  date_variable: Duty Date

---

```{r setup, echo=F}
knitr::opts_chunk$set(echo=F, warning=F, message = F)
```

``` {r}
library(tidyverse)
library(recipes)
library(lubridate)
library(NURS.Data.Quality)
library(caret)

MISSING_TYPES <- c(NA, "", " ", "NA", "nan", "  /  /    ",
                   "NULL", "null", "Null")
# source("make.limited.class.encoder.R")
# source("mining.functions.R")
# source("prepare.data.R")
# source("feature.fit.R")

```

## Rates of missing observations by variable

``` {r results="asis"}

data <- params$path %>% readRDS()
missing <- c(MISSING_TYPES, "  /  /    ", "NULL", "null", "Null")

date.feature <- data[[params$date_variable]] 
location.feature <- data[[params$location_variable]]

missing.data <- data %>% select(-c(params$location_variable, params$date_variable)) %>% 
  is.missing(missing)  
missing.rates <- missing.data %>% apply(2, mean)

for (i in names(missing.rates)){
   cat('\n')  
   cat(glue("{i}: {round(100*missing.rates[i], 3)}%\n"))
   cat("\n")
}

``` 

## Summary of predictability of missing patterns based on location or date

Predictability is measured via the ROC, which ranges from 0.5 to 1, with 1 implying perfect predictability.  Data was divided into training and validation sets - so ROC represents predicatbility on data unseen during training.   Value of > 0.8 may be cuase for concern (see the figures that follow for interpretation of models).

``` {r}

missing.vars <- missing.rates[(missing.rates < 0.2) & (missing.rates > 0.001)] %>% 
  names()

date.missing <- lapply(
  missing.vars,
  function(i) {
    target <- data[[i]] %>% is.missing(missing)
    result <- feature.fit(target, date.feature)
  }
)

location.missing <- lapply(
  missing.vars,
  function(i) {
    target <- data[[i]] %>% is.missing(missing)
    feature.fit(target, location.feature)
  }
)
l <- length(missing.vars)
if ( l > 0){
  frm <- data.frame(
    Var = missing.vars,
    DateROC = sapply(date.missing, function(i) i$AUC)%>% round(3),
    LocROC = sapply(location.missing, function(i) i$AUC)%>% round(3)
  ) 
} else {
  frm <- data.frame(
    Var = NA,
    DateROC = NA,
    LocROC = NA
  )
}

frm %>% knitr::kable(caption="ROC-AUC values for location and date models.")
```

``` {r}
to.group <- function(values, result) {
  values <- values %>% str_replace_all("`", "")
  factor(result$naming_vector[values], levels = result$naming_vector)
}


generate_plot <- function(result, title=NA){
  plotdata <- varImp(result$model) %>% as.data.frame() %>% 
    mutate(Group = to.group(rownames(.), result))
  ncol <- (1 + nrow(plotdata) %/% 16)
  plotdata %>% 
    ggplot(aes(x=Group,  y=Score, color=Group)) + 
    geom_point() + guides(color=guide_legend(ncol=ncol,byrow=FALSE)) + 
    theme(axis.title.x=element_blank(),
                         axis.text.x=element_blank(),
                         axis.ticks.x=element_blank()) + 
    labs(title = title)
}

```

## `r params$date_variable` on Missing

Figures to summarize  Date on missing bias.

``` {r, fig.width=8}
l <- length(missing.vars)
if (l > 0){
  plt <- purrr::map(
    1:l,
    function(i) generate_plot(date.missing[[i]], missing.vars[i]) %>%
      print()
  );
}
```

## `r params$location_variable` on Missing

Figures to summarize Location  on missing bias.

``` {r, fig.width=12}

if (l > 0){ 
  plt <- purrr::map(
    1:l,
    function(i) generate_plot(location.missing[[i]], missing.vars[i]) %>%
      print()
  );
}

```

